Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-18 writing/DraftExposurePaper/DraftExposurePaper.Rmd
add wind exposure table

>>>>

Here is a table of the top 10 storms by number of counties exposed, based on a wind metric of 18 m/s or greater (e.g., tropical storm strength or greater):

all_wind <- county_wind(counties = all_counties, start_year = 1988, 
                        end_year = 2011, wind_limit = 18)

wind_exposed <- all_wind %>%
        group_by(storm_id) %>%
        summarize(number_of_counties_exposed = n()) %>%
        arrange(desc(number_of_counties_exposed)) %>%
        top_n(10)

wind_exposed %>%
        mutate(storm_id = gsub("-", " (", storm_id),
               storm_id = paste0(storm_id, ")")) %>%
        kable(col.names = c("Storm", "# of exposed counties"),
              caption = "Top 10 storms based on the number of counties exposed, using a metric of wind.")
```
#### Is our 3-day window for rian exposure reasonable?

```{r}

```
